Paper Analysis

### 2025-02-13 Paper_WriteUp/Paper_Plots.qmd
update the 1700-1900 perm plot

```{r figure 3 left - plot global parameters for 17-19}
data_path <- here("results_2025/lichess1700-1900")

@@

```{r perm for 17-19}
#| eval: false
perm_data_path <- here("results/lichess1700-1900/perm")

@@

fit_17_19_bullet_prev <- readRDS(file = paste0(
  data_path,
  "/all_rated_bullet_model_prev.RDS"
))

@@

```{r figure 8 left - perm winner effects}
## get the selected users for this, top 20 players
path_id <- 1  ## for 1700-1900
data_path <- all_data_path[path_id]
files <- list.files(data_path)

lichess_data <- files |> 
  map_dfr(~read_player(data_path, .x))

select_users <- bullet_data |> 
  group_by(Username) |> 
  tally() |> 
  arrange(-n) |> 
  ## will change this to n = 20 when run on cluster potentially
  slice_max(order = n, n = 20) |> 
  pull(Username)

## then repeat for the winner effects
player_id <- as_tibble(select_users) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

true_vals <- true_beta |> 
  filter(param == 2) |>  
  mutate(y = row_number() - 0.5,
         yend = y + 1)

perm_17_19_winner <- player_pars |> 
  filter(param == 2) |>
  mutate(y = factor(player_name, levels = levels)) |> 
  ggplot(aes(x = mean, y = y)) +
  stat_histinterval(slab_fill = NA, .width = c(0.5, 0.95)) +
  geom_segment(data = true_vals, 
               aes(x = mean, y = y, yend = yend), col = "red") +
  labs(y = "", x = "Estimated W/L-Effect") +
  theme_single_y()

@@

```{r figure 8 right}
perm_data_path <- here("results/lichessGrandmasters/perm/")

@@

true_vals <- true_beta |> 
  filter(param == 1) |>  
  mutate(y = row_number() - 0.5,
         yend = y + 1)

perm_gm_player <- player_pars |> 
  filter(param == 1) |>
  mutate(y = factor(player_name, levels = levels)) |> 
  ggplot(aes(x = mean, y = y)) +
  stat_histinterval(slab_fill = NA, .width = c(0.5, 0.95)) +
  geom_segment(data = true_vals, 
               aes(x = mean, y = y, yend = yend), col = "red") +
  theme_single_y() +
  labs(x = "Estimated Player Effect", y = "")

>>>>

```{r figure 3 left - plot global parameters for 17-19}
data_path <- here("results/lichess1700-1900_2025")

@@

```{r perm for 17-19}
#| eval: false
perm_data_path <- here("results/lichess1700-1900_2025/perm")

@@

data_path <- here("results/lichess1700-1900_2025")

@@

```{r figure 8 left - perm winner effects}

@@

true_vals <- true_beta |> 
  filter(param == 2) |>  
  mutate(y = factor(player_name, levels = levels)) |> 
  arrange(y) |> 
  mutate(y_fake = row_number() - 0.5,
         yend = row_number() + 0.5)

perm_17_19_winner <- player_pars |> 
  filter(param == 2) |>
  mutate(y = factor(player_name, levels = levels)) |> 
  ggplot(aes(x = mean, y = y)) +
  stat_histinterval(slab_fill = NA, .width = c(0.5, 0.95)) +
  geom_segment(data = true_vals, 
               aes(x = mean, y = y_fake, yend = yend), col = "red") +
  labs(y = "", x = "Estimated W/L-Effect") +
  theme_single_y()

@@

```{r figure 8 right}
perm_data_path <- here("results/lichessGrandmasters_2025/perm/")

@@

true_vals <- true_beta |> 
  filter(param == 1) |>  
  mutate(y = factor(player_name, levels = levels)) |> 
  arrange(y) |> 
  mutate(y_fake = row_number() - 0.5,
         yend = row_number() + 0.5)

perm_gm_player <- player_pars |> 
  filter(param == 1) |>
  mutate(y = factor(player_name, levels = levels)) |> 
  ggplot(aes(x = mean, y = y)) +
  stat_histinterval(slab_fill = NA, .width = c(0.5, 0.95)) +
  geom_segment(data = true_vals, 
               aes(x = mean, y = y_fake, yend = yend), col = "red") +
  theme_single_y() +
  labs(x = "Estimated Player Effect", y = "")
